### 2019-01-07 writing/thesis/chapters/implementation.tex
Escape underscores (fix compilation on travis).

For the actual implementation, we follow \cref{alg:reduce-gobs} but include distributed and shared memory parallelization in the following way:
\begin{itemize}
\item Add vectors \varName{\_globalObservables} and \varName{\_nextGlobalObservables} to all solvers.
  The former stores the observables of the previous timestep, the latter the ones of the current timestep.
  We can thus use the old observables for mesh refinement and compute a new reduction concurrently.
  Before the first timestep, we reset both current and next observables.
  At the beginning of each timestep, we overwrite the previous data with the current data, and reset \varName{\_nextGlobalObservables} with \funName{resetGlobalObservables}.
  This is done in the methods \funName{startNewTimeStep}, \funName{startNewTimeStepFused}, \funName{updateTimeStepSizesFused}, \funName{updateTimeStepSizes}.
\item Reduce global observables in solver with method \funName{reduceGlobalObservables} that takes the \varName{cellInfo} and \varName{solverNumber}.
  The solver number is always 0 because we only use one solver at a given time.
  The cell information stores pointers to the cell data for all solvers.
  We implement this method for all solvers.
  This has the advantage that we have a shared interface for all solver types.
\item Reduce global observables per node in the mappings \className{FinaliseMeshRefinement}, \className{FusedTimeStep}, \className{UpdateAndReduce}.
  \begin{itemize}
  \item We initialize the observables in the method \funName{beginIteration} with \funName{resetGlobalObservables}. 
  \item We reduce the observables in \funName{leaveCell} by calling the solver method \funName{reduceGlobalObservables} with the \varName{cellInfo} of the current cell as argument.
    For the mapping \className{UpdateAndReduce} this is done in the method \funName{enterCell} instead.
  \item If we use \tbb{}, we merge the partially reduced observables in \funName{mergeWithWorkerThread} with \funName{reduceGlobalObservables} using the current reduced observables and the partially reduced observables from the worker.
    This is not necessary for the mapping \className{FinaliseMeshRefinement}.
   \item We update the global observables of the solver in the method \funName{endIteration}, which call the method \funName{updateG}.
  \end{itemize}
\item If we use \mpi{}, we also need to reduce the observables over all ranks.
  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables \varName{_globalObservables}.
  For this, we changed the following methods\todo{Next and current?!} of the \dg{}-solver:
  \begin{itemize}
  \item \funName{compileMessageForMaster} and \funName{sendDataToMaster} to send data from the workers to the master rank.
  \item \funName{mergeWithWorkerData} to merge the received worker data with the current master data. 
  \item \funName{compileMessageForWorker} and \funName{sendDateToWorker} to send the reduced data from the master to the workers.
  \item \funName{mergeWithMasterData} to overwrite the current data of the workers with the reductions from the previous timestep.
  \end{itemize}
  The solvers update the variable \varName{_nextGlobalObservables} during the \mpi{}-reduction.
  Together with the aforementioned resetting of the observables, this again corresponds to \cref{alg:reduce-gobs}.
\end{itemize}
The global observables interface is defined for all solvers, the \mpi{}-reduction only for the \aderdg{}-solver.

>>>>

For the actual implementation, we follow \cref{alg:reduce-gobs} but include distributed and shared memory parallelization in the following way:
\begin{itemize}
\item Add vectors \varName{\_globalObservables} and \varName{\_nextGlobalObservables} to all solvers.
  The former stores the observables of the previous timestep, the latter the ones of the current timestep.
  We can thus use the old observables for mesh refinement and compute a new reduction concurrently.
  Before the first timestep, we reset both current and next observables.
  At the beginning of each timestep, we overwrite the previous data with the current data, and reset \varName{\_nextGlobalObservables} with \funName{resetGlobalObservables}.
  This is done in the methods \funName{startNewTimeStep}, \funName{startNewTimeStepFused}, \funName{updateTimeStepSizesFused}, \funName{updateTimeStepSizes}.
\item Reduce global observables in solver with method \funName{reduceGlobalObservables} that takes the \varName{cellInfo} and \varName{solverNumber}.
  The solver number is always 0 because we only use one solver at a given time.
  The cell information stores pointers to the cell data for all solvers.
  We implement this method for all solvers.
  This has the advantage that we have a shared interface for all solver types.
\item Reduce global observables per node in the mappings \className{FinaliseMeshRefinement}, \className{FusedTimeStep}, \className{UpdateAndReduce}.
  \begin{itemize}
  \item We initialize the observables in the method \funName{beginIteration} with \funName{resetGlobalObservables}. 
  \item We reduce the observables in \funName{leaveCell} by calling the solver method \funName{reduceGlobalObservables} with the \varName{cellInfo} of the current cell as argument.
    For the mapping \className{UpdateAndReduce} this is done in the method \funName{enterCell} instead.
  \item If we use \tbb{}, we merge the partially reduced observables in \funName{mergeWithWorkerThread} with \funName{reduceGlobalObservables} using the current reduced observables and the partially reduced observables from the worker.
    This is not necessary for the mapping \className{FinaliseMeshRefinement}.
   \item We update the global observables of the solver in the method \funName{endIteration}, which call the method \funName{updateG}.
  \end{itemize}
\item If we use \mpi{}, we also need to reduce the observables over all ranks.
  \exahype{} already reduces the timestep size, we extend these already existing \mpi{} messages to also include the global observables \varName{\_globalObservables}.
  For this, we changed the following methods\todo{Next and current?!} of the \dg{}-solver:
  \begin{itemize}
  \item \funName{compileMessageForMaster} and \funName{sendDataToMaster} to send data from the workers to the master rank.
  \item \funName{mergeWithWorkerData} to merge the received worker data with the current master data. 
  \item \funName{compileMessageForWorker} and \funName{sendDateToWorker} to send the reduced data from the master to the workers.
  \item \funName{mergeWithMasterData} to overwrite the current data of the workers with the reductions from the previous timestep.
  \end{itemize}
  The solvers update the variable \varName{\_nextGlobalObservables} during the \mpi{}-reduction.
  Together with the aforementioned resetting of the observables, this again corresponds to \cref{alg:reduce-gobs}.
\end{itemize}
The global observables interface is defined for all solvers, the \mpi{}-reduction only for the \aderdg{}-solver.
